Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Layout experiment, not sure if that is a good idea.

As discussed in \ref{sec:solution-discovery} we use a preprocessor to automatically generate
test drivers.  GHC invokes preprocessors with three arguments.

\begin{description}
    \item[{\tt src}]
        The original source file.  A preprocessor usually does not
        look at the content of this file.  It is only provided, so
        that it can be used in error messages.
    \item[{\tt cur}]
        The file that holds the input for the preprocessor.
    \item[{\tt dst}]
        A path, where the preprocessor should write it's result to.
\end{description}

@@

\begin{quote}
    \emph{TBD: one more example relating to IO is desired.}
\end{quote}

>>>>

As discussed in \ref{sec:solution-discovery}, we use a preprocessor to
automatically generate test drivers.  GHC invokes preprocessors with
three arguments.

\begin{description}
    \item[{\tt src}]
        -- the original source file\\A preprocessor usually does not
        look at the content of this file.  It is only provided, so
        that it can be used in error messages.
    \item[{\tt cur}]
        -- the file that holds the input for the preprocessor
    \item[{\tt dst}]
        -- a path, where the preprocessor should write it's result to
\end{description}

@@
